The ChEMBL database as Linked Open Data

### 2012-07-17 article.tex
Updated the URIs to match linkedchemistry.info

\multicolumn{2}{l}{\textbf{ChEMBL-RDF Prefixes }}\\
act    & http://data.kasabi.com/dataset/chembl-rdf/activity/ \\
assay  & http://data.kasabi.com/dataset/chembl-rdf/assay/ \\
mol    & http://data.kasabi.com/dataset/chembl-rdf/molecule/ \\
res    & http://data.kasabi.com/dataset/chembl-rdf/resource/ \\
\hline
\end{tabular}
\end{center}
\end{table*}

@@

%Mark Davies notes:
%NOTE: Full set of ChEMBL molecules have been created by querying molecule\_dictionary table
%NOTE: I have added extra triple for each molecule: <http://data.kasabi.com/dataset/chembl-rdf/13/molecule/m1> <http://www.w3.org/1999/02/22-rdf-syntax-ns#type> <http://rdf.farmbio.uu.se/chembl/onto/#Molecule> .
%NOTE: Modified molecule compound structure can be queried here: https://wwwdev.ebi.ac.uk/chembl/sparql

@@

\begin{small}
\begin{verbatim}
<http://data.kasabi.com/dataset/chembl-rdf/chemblid/ChEMBL324846>
 skos:exactMatch <http://rdf.chemspider.com/370> .
\end{verbatim}
\end{small}

@@

The Linked Data server used by Bio2RDF has been reconfigured for ChEMBL to provide URL
based services for standard URI resolution, along with text and link searches~\cite{Ansell2011}. 
A Java Web Archive (WAR) file along with the configuration files and build scripts for the ChEMBL-RDF Linked Data server are available on GitHub~\cite{WebAppGitHub}. 
It proxies the standard ChEMBL-RDF URIs by translating URLs between those requested by users and the URIs that are available
in SPARQL endpoints. For example, if the ChEMBL web application is running on the users
local machine, e.g. \url{http://localhost:8080/chembl/}, then a request for the
article with identifier ``a31863'', \url{http://localhost:8080/-chembl/article/a31863},
will be resolved from the database using the full original URI,
\url{http://data.kasabi.com/dataset/chembl-rdf/activity/a31863}. If the
user requested an RDF document using content negotiation, the original URIs will be unchanged,
however, if the user requested an HTML document, the results will contain both the
original RDF triples, represented using RDFa, with links that resolve using the users local machine.

>>>>

\multicolumn{2}{l}{\textbf{ChEMBL-RDF Prefixes }}\\
act    & http://linkedchemistry.info/chembl/activity/ \\
assay  & http://linkedchemistry.info/chembl/assay/ \\
mol    & http://linkedchemistry.info/chembl/molecule/ \\
res    & http://linkedchemistry.info/chembl/resource/ \\
\hline
\end{tabular}
\end{center}
\end{table*}

@@

%Mark Davies notes:
%NOTE: Full set of ChEMBL molecules have been created by querying molecule\_dictionary table
%NOTE: I have added extra triple for each molecule: <http://linkedchemistry.info/chembl/13/molecule/m1> <http://www.w3.org/1999/02/22-rdf-syntax-ns#type> <http://rdf.farmbio.uu.se/chembl/onto/#Molecule> .
%NOTE: Modified molecule compound structure can be queried here: https://wwwdev.ebi.ac.uk/chembl/sparql

@@

\begin{small}
\begin{verbatim}
<http://linkedchemistry.info/chembl/chemblid/ChEMBL324846>
 skos:exactMatch <http://rdf.chemspider.com/370> .
\end{verbatim}
\end{small}

@@

The Linked Data server used by Bio2RDF has been reconfigured for ChEMBL to provide URL
based services for standard URI resolution, along with text and link searches~\cite{Ansell2011}. 
A Java Web Archive (WAR) file along with the configuration files and build scripts for the ChEMBL-RDF Linked Data server are available on GitHub~\cite{WebAppGitHub}. 
It proxies the standard ChEMBL-RDF URIs by translating URLs between those requested by users and the URIs that are available
in SPARQL endpoints. For example, if the ChEMBL web application is running on the users
local machine, e.g. \url{http://localhost:8080/chembl/}, then a request for the
article with identifier ``a31863'', \url{http://localhost:8080/-chembl/article/a31863},
will be resolved from the database using the full original URI,
\url{http://linkedchemistry.info/chembl/activity/a31863}. If the
user requested an RDF document using content negotiation, the original URIs will be unchanged,
however, if the user requested an HTML document, the results will contain both the
original RDF triples, represented using RDFa, with links that resolve using the users local machine.
